\chapter{Related Work}
\section{Brain Imaging DataStructure}
what why what it looks like

\section{MRI Processing/Registration Tools}
FSL, SPM, ANTS, FreeSurfer

\section{Quantitative MRI using bSSFP}
Some bla bla about qMRI development in the past. \\
In depth description of sequence, profile, banding
\subsection{Configuration Modes \& Asymmetry Maps}
karla miller paper

\subsection{T1 and T2 Map Estimation using MIRACLE}
TESS \& MIRACLE papers

\section{Deep Learning in Medical Imaging and MRI}
UNet, challenges, impact of transformers, ...


\chapter{Methods}\label{\positionnumber} 
\section{The Dove Dataset}
Some stats on size 
\subsection{Participants \& Study Design}
briefly describe participants, task, scanning times (of the day)

\subsection{Recorded Sequences}
cf gais doc.
Details on acquisitions

\section{Processing Pipeline}
requirements
\subsection{bSSFP}
\subsection{Phase Correction}
Why, how

\subsubsection{Motion Correction \& Co-Registration}
\paragraph{Initial FSL Pipeline} motion correction to first. Direct, inverse to t1w, B1, T1w rescaling. Difficulties with artefacts, special requirements due to quanti, auto scaling of registered image

\paragraph{SPM Pipeline} exact steps that spm executes. difficulties with docs, lack of API


\subsection{DWI}
TODO ask svenja what was done


\section{Machine Learning-based DWI Tensor estimation from bSSFP data}
MONAI, torchio, pytorch lightning. 

\subsection{Baseline}
UNet + some extra layers to fit output dim. 

\subsection{Augmentation}

\subsection{PreTraining}
Sparse data, small batch sizes. => Augmentation not enough => Pre training
\paragraph{AutoEncoder PreTraining}
As auto encoder. train autoenc for bssfp only 

\paragraph{ExtraHead Transfer and Fine tuning}
freeze autoenc, add head. transfer then unfreeze all and fine tune
Unet + extra head

\subsection{Complex vs. non-complex}
input and weights 









